\documentclass[10pt]{article}

% small margins
\usepackage[margin=0.9in]{geometry}

% no large spaces in lists
\usepackage{enumitem}
\setlist{nolistsep}

\title{\vspace{-4em}6.S078 Update}
\author{Troy Astorino \and Turner Bohlen \and Craig Cheney \and Gus Downs}

\begin{document}
\maketitle
\vspace{-4em}

\section{Plan Progress}
The plan has not significantly progressed since the last update. We applied to
the Founders' Skills Accelerator, and are meeting with the Bolt founder on
Thursday to discuss that accelerator. We haven't written in updates on future
team status, so that may be valuable information to include. Craig, Troy, and
Gus are all committed to working during the summer (Turner has a previous
commitment), and Troy is planning on working continuing full time work into the
fall.  We believe we need to recruit an additional programmer for the summer
(and hopefully beyond) in order to ensure that software won't be a bottleneck on
prototype development. We are planning on waiting until we hear back from
accelerators before recruiting this additional programmer, so that we can
recruit from a stronger position.

On the suggestion of Professor Gifford, we're going to put together a five year
financial model.  That should both add a valuable perspective and be fun.

\section{Prototype Progress}
On the software side, we've had some difficulties integrating with the Point
Cloud Library, which stalled our advance on point cloud processing for a time.
We've mostly overcome those at this point, and are moving forward with point
cloud cleaning,  meshing, etc. Because of this delay, we don't have a scan
visualization to show (we had hoped to), but should by next week.

On the hardware end, we've ordered some gratings and LEDs, and some CMOS arrays
to build cameras on top of.

\section{Baffling Variables}
Execution is still number most significant.

In terms of forward progress, the best way to go about finding another team
member is a bit of a question. Since we decided to wait on accelerator
applications before starting, we haven't thought particularly hard about it yet,
but it could be perplexing. It seems the best options would be to find an friend
or friend-of-a-friend, or to email out to CSAIL find someone there. One
currently confusing issue is whether it is a good idea to wait to recruit until accelerator
decisions are made. On the one hand a more secure funding situation would be
more attractive to more people, and so may expose some better candidates. On the
other, the longer we wait the more people are committed to other
positions. 

\section{Seven Day Plan}
\begin{itemize}
  \item Make a 5 year financial model.
  \item Continue software development, focusing on meshing and visualization, and
    then swept-plane scanning if those are complete
  \item Test if basic grating option will work for projection (i.e. see whether
    it creates lines with a dark enough contrast)
  \item Continue embedded development (integrating cameras with microcontrollers)
\end{itemize}

\section{People to Meet}
N/A

\section{Desired Resources}
N/A

\end{document}