\documentclass[10pt]{article}

% small margins
\usepackage[margin=1in]{geometry}

% no large spaces in lists
\usepackage{enumitem}
\setlist{nolistsep}

\title{\vspace{-4em}6.S078 Update}
\author{Troy Astorino \and Turner Bohlen \and Craig Cheney \and Gus Downs}

\begin{document}
\maketitle
\vspace{-4em}

\section{Plan Progress}
We had 2 interviews for the MIT Founders' Skills Accelerator in the past 3 days,
and so spent a lot of time preparing for those. We are awaiting the results of
the application. We got good feedback from both the interview and on the paper
application, but may need adjust our plan accordingly.

We did complete a rough financial model which we sent to Professor Gifford, and
are excited to get feedback on it.

\section{Prototype Progress}
With the interviews and the rest of the craziness this week, we have not made a
large amount of prototype progress this week. We have ordered more parts for a
laser projection system, and on the hardware end Craig is close to having our
board taking camera images. We have made some progress on the meshing front.

\section{Baffling Variables}
We are somewhat unsure of the size of the consumer market.  We think that there
is market potential there, but are unsure of how much VCs would be convinced of
that potential. We think there is some possibility that we'll have to switch
target market segment.

\section{Seven Day Plan}
\begin{itemize}
\item Continue development of the meshing system
\item Put together projection assembly once the pieces arrive
\item Take images from the board to a computer
\end{itemize}
\section{People to Meet}

\section{Desired Resources}

\end{document}